Optimal forward modeling of gravitational fields using tesseroids with adaptive discretization

### 2014-09-10 body.tex
Few more sentences in shell section

\noindent
where $r$ is the radial coordinate of the computation point and
$r_1$ and $r_2$ are radial coordinates
of the bottom and top of the spherical shell, respectively.
Table~\ref{tab:shell} summarizes the parameters defining the spherical shell.

@@

Because of that, comparing the shell and tesseroid effects at a single point
would not be representative of the actual error committed.

@@

We perform the computations for the tesseroid model on an $11 \times 11$ point regular grid.

@@

The grid is located at a constant height $h = 1\ km$ above the spherical shell.

The computations where repeated for discretization into tesseroids of sizes $S = 1^\circ$, $2^\circ$,
$5^\circ$, and $30^\circ$.

@@

\begin{table}
    \caption{Reference values of the gravitational potential, attraction, and
    gravity gradient tensor of the spherical shell.}
    \label{tab:shell-data}
    \begin{tabular}{ll}
        $V$                    &    $14278.021191\ m^2.s^{-2}$ \\
        $g_z$                  &    $223.788630$ mGal \\
        $g_{xx} = g_{yy}$      &    $-0.350758$ E\"otv\"os\\
        $g_{zz}$               &    $0.701517$ E\"otv\"os\\
    \end{tabular}
\end{table}

@@

The recursive division algorithm described above
is implemented in the software package
Tesseroids.
The package consists
of command-line programs
written in the C programming language.
Tesseroids is open-source software
and is freely available
on the internet\footnote{www.leouieda.com/tesseroids}
\textbf{CITE ARCHIVE} provides a persistent
archive for the source code.

@@

Meh.

>>>>

\noindent
where $r$ is the radial coordinate of the computation point and
$r_1$ and $r_2$ are radial coordinates
of the bottom and top of the spherical shell, respectively.
Table~\ref{tab:shell} summarizes the parameters defining the spherical shell.
Table~\ref{tab:shell-data} contains the values of the gravitational potential,
attraction, and gravity gradient tensor for such a shell computed at a height
$h = 1\ km$ above the shell.

@@

Because of that, comparing the shell and tesseroid effects at a single point
would not be representative of the actual error.

@@

We performed the computations for the tesseroid model on an $11 \times 11$ point regular grid.

@@

The grid was located at a constant height $h = 1\ km$ above the spherical shell.

We can take the error in the computation as the maximum absolute difference between the
value calculated for the spherical shell and the corresponding value for the
tesseroid model.

The above computations were repeated for tesseroids of sizes $S = 1^\circ$, $2^\circ$,
$5^\circ$, and $30^\circ$ to verify if the result depends on the discretization.

@@

\begin{table}
    \caption{Reference values of the gravitational potential, attraction, and
    gravity gradient tensor of the spherical shell.}
    \label{tab:shell-data}
    \begin{tabular}{ll}
        $V$                                         &  $14278.021191\ m^2.s^{-2}$ \\
        $g_z$                                       &  $223.788630$ mGal \\
        $g_{xx}$, $g_{yy}$                          &  $-0.350758$ E\"otv\"os\\
        $g_{zz}$                                    &  $0.701517$ E\"otv\"os\\
        $g_x$, $g_y$, $g_{xy}$, $g_{xz}$, $g_{yz}$  &  $0$\\
    \end{tabular}
\end{table}

@@

The recursive division algorithm described above
is implemented in the software package
Tesseroids.
The package consists
of command-line programs
written in the C programming language.
Tesseroids is open-source software
and is freely available
on the Internet\footnote{leouieda.com/tesseroids}
\textbf{CITE ARCHIVE} provides a persistent
archive for the source code.

@@
